---
title: "pipe"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
data(diamonds, package='ggplot2')
```

### Preview the first five rows
```{r}
head(diamonds)
```
### Using the pipe (%>%) operator
```{r}
# Keyboard shortcut is Ctrl+Shift+M (Cmd+Shift+M in Macs)
# Preview the first five rows using pipes
diamonds %>% head(5)
```

### Select columns
```{r}
select(diamonds, carat, color, price)
```

### Use piping to select columns
```{r}
diamonds %>% select(carat, price)
```

### Filter rows for data
```{r}
filter(diamonds, cut=='Premium')
```

### Filter using piping
```{r}
diamonds %>% filter(cut=='Premium')
```

### Filter for multiple conditions
```{r}
diamonds %>% filter(cut=='Premium' & carat > 0.30)
```
### Group by cuts, then summarize the mean price by cut
```{r}
cut_group <- group_by(diamonds, cut)
summarize(cut_group, mean(price))
```

### Use pipes to group by cuts, then summarize the mean price by cut
```{r}
diamonds %>% group_by(cut) %>% summarise(mean(price))
```

### In addition to the above, return total price by cut
```{r}
diamonds %>% 
  group_by(cut) %>% 
  summarize(mean(price), sum(price))
```
### A nested, messier version that accomplishes the same task
```{r}
summarize(group_by(diamonds, cut), mean(price), sum(price))
```

