---
title: "Pipe Dreams Are Made of These"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Dependency
```{r}
library(tidyverse)
```
### Read CSV file
```{r}
students <-read_csv("students.csv")
```
### Preview tibble
```{r}
students %>% head()
```

### A list of all schools
```{r}
# unique(dataset, variable) displays unique elements from that column
#unique(students$school_name)

# Your code here
students$school_name %>% unique()
```

### Calculate the total count of schools
```{r}
# school_count <- unique(students$school_name)
# Use length() to identify the number of schools
#length(school_count)
#paste("There are", length(school_count), "schools")

# Your code here
students$school_name %>% 
  unique() %>% 
  length()
```

### Calculate the total number of students
```{r}
# nrow() returns the number of rows
student_count <-  students %>% nrow()
paste("There are a total of", student_count, "students.")
```

### Calculate the average reading and math scores
```{r}
mean_reading_score <- summarize(students, mean(reading_score))
paste("The average reading score is", mean_reading_score)

mean_math_score <- summarize(students, mean(math_score))
paste("The average math score is", mean_math_score)
```
### Calculate the percentage of students with passing reading scores, i.e. over 70%.
```{r}
#passing_reading <- filter(students, reading_score > 70)
#passing_reading_count <- nrow(passing_reading)
#percentage_passing_reading <- passing_reading_count*100 / student_count
#percentage_passing_reading <- round(percentage_passing_reading,2)

# Your code here
percentage_passing_reading <- students %>% 
  filter(reading_score > 70) %>% 
  nrow() * 100 / student_count %>% 
  round(2)

percentage_passing_reading
```
### Calculate the percentage of students with passing math scores, i.e. over 70%.
```{r}
# passing_math <- filter(students, math_score > 70)
# passing_math_count <- nrow(passing_math)
# percentage_passing_math <- passing_math_count*100 / student_count
# percentage_passing_math <- round(percentage_passing_math, 2)
# paste(percentage_passing_math, "% of the students have passing math scores.")

# Your code here
percentage_passing_math <-  students %>% 
  filter(math_score > 70) %>% 
  nrow() * 100 / student_count %>% 
  round(2)

percentage_passing_math
```
### Calculate the overall passing rate, i.e. the average of math and reading passing percentages
```{r}
overall_passing_rate <- (percentage_passing_math + percentage_passing_reading) / 2
overall_passing_rate
```

### Calculate the average math and reading scores by school
```{r}
# school_grouping <- group_by(students, school_name)
# summarize(school_grouping, avg.reading=mean(reading_score), avg.math = mean(math_score))

# Your code here
students %>% 
  group_by(school_name) %>% 
  summarize(avg.reading=mean(reading_score), avg.math=mean(math_score))
```

### Calculate the average math and reading scores by grade level at each school
```{r}
# grade_grouping <- group_by(students, school_name, grade)
# summarize(grade_grouping, avg.reading=mean(reading_score), avg.math=mean(math_score))

# Your code here
students %>% 
  group_by(school_name, grade) %>% 
  summarize(avg.reading=mean(reading_score), avg.math=mean(math_score))
```
